\documentclass[11pt,fleqn]{article}

\setlength {\topmargin} {-.15in}
\setlength {\textheight} {8.6in}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usetikzlibrary{automata,positioning,arrows}
\usepackage{diagbox}
%\usepackage{ulem}
\usepackage{stackrel}

\renewcommand{\labelenumii}{\theenumii.}

\newcommand{\mname}[1]{\mbox{\sf #1}}
\newcommand{\pnote}[1]{{\langle \text{#1} \rangle}}
\newcommand{\set}[1]{{\{ #1 \}}}
\newcommand{\sB}{\mbox{$\cal B$}}
\newcommand{\sC}{\mbox{$\cal C$}}
\newcommand{\sF}{\mbox{$\cal F$}}
\newcommand{\sH}{\mbox{$\cal H$}}
\newcommand{\sM}{\mbox{$\cal M$}}
\newcommand{\sP}{\mbox{$\cal P$}}
\newcommand{\sV}{\mbox{$\cal V$}}
\newcommand{\TRUE}{\mbox{{\sc t}}}
\newcommand{\FALSE}{\mbox{{\sc f}}}
\newcommand{\Neg}{\neg}
\newcommand{\Implies}{\Rightarrow}
\renewcommand{\And}{\wedge}
\newcommand{\Or}{\vee}
\newcommand{\ForallApp}{\forall\,}
\newcommand{\ForsomeApp}{\exists\,}
\newcommand{\mdot}{\mathrel\bullet}
\newcommand{\der}[2]{\stackrel[#2]{#1}{\longrightarrow}}

\begin{document}

\begin{center}

  {\large \textbf{COMPSCI/SFWRENG 2FA3}}\\[2mm]
  {\large \textbf{Discrete Mathematics with Applications II}}\\[2mm]
  {\large \textbf{Winter 2018}}\\[8mm]
  {\huge \textbf{Assignment 10}}\\[6mm]
  {\large \textbf{Dr.~William M. Farmer}}\\[2mm]
  {\large \textbf{McMaster University}}\\[6mm]
  {\large Revised: March 25, 2018}

\end{center}

\medskip

Assignment 10 consists of two required problems and one optional bonus
problem.  You are required to write your solutions using LaTeX.

Submit the following files to the Assignment 10 folder on Avenue under
Assessments/Assignments:

\begin{enumerate}

  \item A file named \texttt{Assignment\_10\_\emph{YourMacID}.tex} that
    is a copy of the LaTeX source file for this assignment
    (\texttt{Assignment\_10.tex}) with your solutions entered after
    each problem.  \texttt{\emph{YourMacID}} must be your personal
    MacID.

  \item A file named \texttt{Assignment\_10\_\emph{YourMacID}.pdf} that
    is the PDF output produced by executing

    \begin{itemize}

      \item[] \texttt{pdflatex Assignment\_10\_\emph{YourMacID}}

    \end{itemize}

  \item Any additional files that are needed to produce the PDF
    output.  These should be given names that begin with
    \texttt{Assignment\_10\_\emph{YourMacID}\_}\ .

\end{enumerate}

\noindent
This assignment is due \textbf{Sunday, April 1, 2018 before midnight.}
You must write your name and MacID at the bottom of the LaTeX file.
You are allowed to submit the assignment multiple times, but only the
last submission will be marked.  \textbf{Late submissions and files
  that are not named exactly as specified above or are missing your
  name or MacID will not be accepted!}

\textbf{Although you are allowed to receive help from the
  instructional staff and other students, your submitted program must
  be your own work.  Copying will be treated as academic dishonesty!}

\newpage

\subsection*{Required Problems}

\begin{enumerate}

  \item \textbf{[10 points]} Construct a regular grammar that
    generates the language matched by the regular expression $(000^* +
    111^*)^*$.

  \bigskip

   A possible regular grammar that generates the language matched by the above expression is denoted by G:\\
  
   G = (\{S, A, B, C, D, E, F \}, \{0, 1\}, P, S)\\
   Where P is the set of productions below 
    $S \Rightarrow  A | B | \epsilon \\
    A  \Rightarrow 0C \\
    B \Rightarrow 1D \\
    C  \Rightarrow 0E \\
    E \Rightarrow 0E | \epsilon | S \\
    D \Rightarrow 1F \\
    F  \Rightarrow 1F | \epsilon | S$

  \bigskip

  \item \textbf{[10 points]} Let $\Sigma = \set{a,b}$ and $L = \set{x
    \in \Sigma^* \mid x \not= \mname{rev}\ x}$.  Construct a simple
    grammar for $L$ as well as grammars in Chomsky and Greibach normal
    form for $L$.

  \bigskip

  \textbf{Put your three grammars here.}  

\end{enumerate}

\subsection*{Bonus Problem}

\begin{itemize}

  \item[] \textbf{[5 bonus points]} Prove that, if a CFG $G$ is right
    linear, then $L(G)$ is regular.

  \bigskip

  \textbf{Put your proof here.} 

\end{itemize}

\subsection*{Name and MacID}

\medskip

Name: \textbf{Alexie McDonald}

\bigskip

\noindent
MacID: \textbf{mcdona16}

\end{document}


